---
title: "HW1"
output: github_document
author: Ruohan Lyu
---

# Problem 1
## Load the Library and Dataset

```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

## Describe the Dataset

The variables included in this dataset are: `r paste(names(early_january_weather), collapse = ", ")`. Some important variables are `temp`, `humid`, and `time_hour`, which will be used to create a scatterplot in the next step.

This dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature for the dataset is `r mean(early_january_weather$temp, na.rm = TRUE)`.

## Scatterplot
### Create the Scatterplot

```{r}
weather_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() + 
  labs(title = "Temperature vs Time_hour in Early January", 
       x = "Time_hour",
       y = "Temperature",
       color = "Humidity")
weather_plot
```

### Save the Plot

```{r}
ggsave("scatterplot.png", plot = weather_plot, width = 8, height = 6)
```

# Problem 2
## Create Data Frame

```{r}
random_sample = rnorm(10)
```

```{r}
my_dataframe = data.frame(
  random_sample,
  logical_vector = random_sample > 0,
  character_vector = c("cat","dog","bird","fish","ant","bee","cow","duck","lion","tiger"),
  factor_vector = factor(c("A","B","C","A","B","C","A","B","C","A"))
)
my_dataframe #print the data frame
```

## Take the Mean
```{r}
mean(pull(my_dataframe, random_sample))
mean(pull(my_dataframe, logical_vector))
mean(pull(my_dataframe, character_vector))
mean(pull(my_dataframe, factor_vector))
```

According to the results, the mean of `random_sample` and `logical_vector` can be calculated as `r mean(pull(my_dataframe, random_sample))` and `r mean(pull(my_dataframe, logical_vector))` (defined as 0 or 1). However, attempting to compute the mean of the other two vectors returns `NA`.

## Apply the as.numeric Function
```{r}
numeric_logical <- as.numeric(pull(my_dataframe, logical_vector))
numeric_character <- as.numeric(pull(my_dataframe, character_vector))
numeric_factor <- as.numeric(pull(my_dataframe, factor_vector))
```

Logical variables can be automatically converted into numbers (TRUE = 1, FALSE = 0), which allows us to calculate the mean. Factor variables can also be converted to numbers using the as.numeric function; however, the resulting mean has no real interpretive meaning. Finally, character variables cannot be converted to numbers, so it is impossible to take the mean. 

All these results explain why the mean of random_sample and logical_vector can be calculated, while attempting to take the mean of character or factor variables either fails or produces meaningless values.
