---
title: "HW1"
output: github_document
author: Ruohan Lyu
---

# Load the Library and Dataset

```{r}
library(moderndive)
library(ggplot2)
data("early_january_weather")
```

# Describing the Dataset
## early_january_weather

The variables included in this dataset are: `r paste(names(early_january_weather), collapse = ", ")`. Some important variables are temp, humid, and time_hour, which will be used to create a scatterplot in the next step.

This dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature for the dataset is `r mean(early_january_weather$temp, na.rm = TRUE)`.

# Making a scatterplot
## Load ggplot2

```{r}
library(ggplot2)
```

## Scatterplot

```{r}
weather_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() + 
  labs(title = "Temperature vs Time_hour in Early January", 
       x = "Time_hour",
       y = "Temperature",
       color = "Humidity")
weather_plot
```




