---
title: "HW1"
output: github_document
author: Ruohan Lyu
---

# Problem 1
## Load the Library and Dataset

```{r}
library(moderndive)
library(ggplot2)
data("early_january_weather")
```

## Describing the Dataset
### early_january_weather

The variables included in this dataset are: `r paste(names(early_january_weather), collapse = ", ")`. Some important variables are temp, humid, and time_hour, which will be used to create a scatterplot in the next step.

This dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature for the dataset is `r mean(early_january_weather$temp, na.rm = TRUE)`.

## Making a scatterplot
### Load ggplot2

```{r}
library(ggplot2)
```

### Scatterplot

```{r}
weather_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() + 
  labs(title = "Temperature vs Time_hour in Early January", 
       x = "Time_hour",
       y = "Temperature",
       color = "Humidity")
weather_plot
```

### Saving the Plot

```{r}
ggsave("scatterplot.png", plot = weather_plot, width = 8, height = 6)
```

# Problem 2
## Create a Data Frame
### Four Factors
**1. a random sample of size 10 from a standard Normal distribution**
```{r}
random_sample = rnorm(10)
```

**2. a logical vector indicating whether elements of the sample are greater than 0**
```{r}
logical_vector = ifelse(random_sample > 0, "yes", "no")
```

**3. a character vector of length 10**
```{r}
character_vector = c("cat","dog","bird","fish","ant","bee","cow","duck","lion","tiger")
```

**4. a factor vector of length 10, with 3 different factor “levels”**
```{r}
factor_vector = factor(c("A","B","C","A","B","C","A","B","C","A"))
```

### Data Frame
```{r}
my_dataframe = data.frame(
  random = random_sample,
  logical = logical_vector,
  character = character_vector,
  factor = factor_vector
)
my_dataframe #print the data frame
```

